---
title: "How to Make Plots with GGPlot"
author: "Barry DeCicco"
date: '2022-10-15'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Setting up libraries

```{r load-libraries, echo = TRUE}

library(ggplot2)
library(magrittr)
library(tidyverse)
library(kableExtra)
library(readr)
library(janitor)
library(stringr)
library(lubridate)
library(zoo)


```


# Data Set

## Load Data from Dropbox

```{r load-date-from-dropbox}

Big_Mart_df <- read.csv("https://www.dropbox.com/s/a7awmqghrb2m145/Big%20Mart%20Dataset%20-%20Sheet1.csv?dl=1")

```



## Examine Data

### Print the first/last rows of the Big Mart data frame?

```{r examine-data-1}

head(Big_Mart_df)
tail(Big_Mart_df)


```

### What are the column names of the Big Mart data frame?

```{r examine-data-2}

names(Big_Mart_df)

```

### What are the classes of the Big Mart data frame?

```{r examine-data-3}
lapply(Big_Mart_df, class)

```

