---
title: "Run Analyses"
author: "Barry DeCicco"
date: "`r format(Sys.time(), '%Y-%m-%d, %H:%M:%S %Z')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    code_folding: hide
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
---

```{r setup-}

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)

# Declare path to this script relative to the project root directory.
here::i_am(
  path = "inst/Run-Analyses.Rmd"
  )

```



```{r load-packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

library(emmeans)    # for emmeans
library(lme4) 
library(flextable)  # for tables with .rtf output
library(psych)      # for ICC
library(magrittr)
library(rmarkdown)  # For pandoc_version()
library(Hmisc)      # for label()
library(here)       # for here()
library(devtools)   # for session_info()
# library(TFCBTLS)    # for git_report()

library(kableExtra) # for pretty tables
library(tidyquant)  # for date conversions - zoo()

library(pastecs)    # for stat.desc
library(tidyverse)

library(readxl)     # For reading in .xlsx and .xsl files, without using Java.
# library(xlsx)       # to import from Excel (cohort dates)


library(janitor)    # for the tabyl command  (nice tables)

library(stringr)    # string work, such as st_detect()

require(gridExtra)  # for printing a grid of plots.

library(broom)      # both of these are for getting nice output
library("tidyr")    # from linear mixed models.

library("cstatpower")
library("ggplot2")
library("effectsize")
library(hrbrthemes)  # for theme_ipsum()


library(foreign)    # for importing SPSS data sets.
library(robustbase) # for robust MH distances
library(rrcov)

```

#  Load the Data

```{r load-Main_Data}


load(file = here::here("data/Main_Data.Rdata"))

```


```{r}

```




```{r make-count-tables, eval=FALSE}


# Overview of Data:

# Counts:
# 
# * Count of unique patients (by MRN)
# * Count of unique visits (by Epic CSN)
# * Counts by Sex
# * Counts by Race (FirstRace)
# * Counts by Alcohol Withdrawal
# * Counts by CHF
# * Counts by Period (Pre-, Post-COVID)
# * 
# 
# Summaries of Continuous Variables:
# 
# * Age



Main_Data <- dplyr::filter()


ALCWD_CHF_Case_period_table <- Main_Data %>%
  tabyl(ALCWD_CHF_Case,Period) %>% 
  adorn_totals("row") %>% 
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )

View(ALCWD_CHF_Case_period_table)

Sex_Case_period_table <- Main_Data %>%
  tabyl(Sex,Period) %>% 
  adorn_totals("row") %>% 
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )
View(Sex_Case_period_table)


Sex_Case_ALC_period_tabyl <- Main_Data %>%
  tabyl(ALCWD_CHF_Case, Sex,Period) %>% 
  adorn_totals("row") %>% 
  as.data.frame()
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )
View(Sex_Case_ALC_period_tabyl)
class(Sex_Case_ALC_period_tabyl[1])


post_ALCWD <- as.data.frame(Sex_Case_ALC_period_tabyl[1]) %>% 
  dplyr::rename(ALCWD = Post.Covid.ALCWD_CHF_Case) %>% 
    dplyr::mutate(`Percent-Post-Male` = round(200*Post.Covid.Male/sum(Post.Covid.Male),0),
                `Percent-Post-Female` = round(200*Post.Covid.Female/sum(Post.Covid.Female),0)
  ) %>% 
  dplyr::select(ALCWD,Post.Covid.Male, `Percent-Post-Male`, Post.Covid.Female,`Percent-Post-Female` )


pre_ALCWD <- as.data.frame(Sex_Case_ALC_period_tabyl[2]) %>% 
  dplyr::rename(ALCWD = Pre.Covid.ALCWD_CHF_Case) %>% 
      dplyr::mutate(`Percent-Pre-Male` = round(200*Pre.Covid.Male/sum(Pre.Covid.Male),0),
                `Percent-Pre-Female` = round(200*Pre.Covid.Female/sum(Pre.Covid.Female),0)
  ) %>% 
  dplyr::select(ALCWD,Pre.Covid.Male, `Percent-Pre-Male`, Pre.Covid.Female,`Percent-Pre-Female` )

Sex_Case_ALC_period_table <- dplyr::left_join(pre_ALCWD,post_ALCWD, by= "ALCWD")




```




```{r make-summary-tables, eval=FALSE}

# CHANGE CODE TO COVER CONTINUOUS VARIABLES:
  
# AGE,
# los inpatient
# WHAT ELSE?


ALCWD_CHF_Case_period_table <- Main_Data %>%
  tabyl(ALCWD_CHF_Case,Period) %>% 
  adorn_totals("row") %>% 
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )

View(ALCWD_CHF_Case_period_table)

Sex_Case_period_table <- Main_Data %>%
  tabyl(Sex,Period) %>% 
  adorn_totals("row") %>% 
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )
View(Sex_Case_period_table)


Sex_Case_ALC_period_tabyl <- Main_Data %>%
  tabyl(ALCWD_CHF_Case, Sex,Period) %>% 
  adorn_totals("row") %>% 
  dplyr::mutate(`Percent-Post` = round(200*`Post-Covid`/sum(`Post-Covid`),0),
                `Percent-Pre` = round(200*`Pre-Covid`/sum(`Pre-Covid`),0)
  )
View(Sex_Case_ALC_period_tabyl)
class(Sex_Case_ALC_period_tabyl[1])


post_ALCWD <- as.data.frame(Sex_Case_ALC_period_tabyl[1]) %>% 
  dplyr::rename(ALCWD = Post.Covid.ALCWD_CHF_Case) %>% 
    dplyr::mutate(`Percent-Post-Male` = round(200*Post.Covid.Male/sum(Post.Covid.Male),0),
                `Percent-Post-Female` = round(200*Post.Covid.Female/sum(Post.Covid.Female),0)
  ) %>% 
  dplyr::select(ALCWD,Post.Covid.Male, `Percent-Post-Male`, Post.Covid.Female,`Percent-Post-Female` )


pre_ALCWD <- as.data.frame(Sex_Case_ALC_period_tabyl[2]) %>% 
  dplyr::rename(ALCWD = Pre.Covid.ALCWD_CHF_Case) %>% 
      dplyr::mutate(`Percent-Pre-Male` = round(200*Pre.Covid.Male/sum(Pre.Covid.Male),0),
                `Percent-Pre-Female` = round(200*Pre.Covid.Female/sum(Pre.Covid.Female),0)
  ) %>% 
  dplyr::select(ALCWD,Pre.Covid.Male, `Percent-Pre-Male`, Pre.Covid.Female,`Percent-Pre-Female` )

Sex_Case_ALC_period_table <- dplyr::left_join(pre_ALCWD,post_ALCWD, by= "ALCWD")




```




```{r table-ED-lcoation-vs-hospital-location-I, eval = FALSE}

with(Main_Data, table(AdmissionLocationName, EdLocationName, useNA = 'always'))

department_df <- Main_Data %>% 
  dplyr::group_by(AdmissionDepartmentName, EdDepartmentName) %>% 
  tally() %>% 
  as.data.frame() %>% 
  dplyr::arrange(desc(n))


View(department_df)

```



```{r examine-matched-data-sets, eval = FALSE}

dim(Main_Data)

with(Main_Data, table(EncounterEpicCsn, useNA = 'always'))
with(Main_Data, table(Icd10, useNA = 'always'))   


Main_Data %>% 
  dplyr::group_by(EncounterEpicCsn) %>% 
  tally() %>% 
  as.data.frame() %>% 
  dplyr::rename(Count = n) %>% 
  dplyr::arrange(desc(Count)) %>% 
  dplyr::mutate(Proportion = format(round(Count/dim(Main_Data)[1],5), nsmall = 5))


 
```


```{r examine-ChfIndicatedInEncounter, eval = FALSE}

chf_table_df <- Main_Data %>% 
  dplyr::filter(ChfIndicatedInEncounter == 1) %>% 
  dplyr::group_by(Icd10, Name) %>% 
  tally() %>% 
  as.data.frame() %>% 
  dplyr::arrange(desc(n))

View(chf_table_df)
```



```{r examine-AlcoholWithdrawIndicatedInEncounter, eval = FALSE}

alc_table_df <- Main_Data %>% 
  dplyr::filter(AlcoholWithdrawIndicatedInEncounter == 1) %>% 
  dplyr::group_by(Icd10, Name) %>% 
  tally() %>% 
  as.data.frame() %>% 
  dplyr::arrange(desc(n))

View(alc_table_df)
```


```{r table-Acohol-withdrawal-vs-Chf, eval=FALSE}

with(Main_Data, table(AlcoholWithdrawIndicatedInEncounter, ChfIndicatedInEncounter, useNA = 'always'))


```

## Examine Locations and Departments:

ED Location Names vs Hospital Location Names,
ED Department vs Hospital Admitting Department.


```{r table-ED-lcoation-vs-hospital-location-II, eval = FALSE}

with(Main_Data, table(AdmissionLocationName, EdLocationName, useNA = 'always'))

location_df <- Main_Data %>% 
  dplyr::group_by(AdmissionLocationName, EdLocationName) %>% 
  tally() %>% 
  as.data.frame() %>% 
  dplyr::arrange(desc(n))

View(location_df)

```


# Plots

## ED Arrivals and Admission **Counts** by Week, flagged by pre-/post-COVID.


### Plot ED Arrivals by Date, flagged by pre-/post-COVID.

```{r plot-ED-weekly-arrivals-with-period-flag}

# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

ED_Visit_Data <- Main_Data %>% 
  dplyr::group_by(Period, week = as.Date(cut(EdArrivalDate, "week"))) %>% 
  tally()
  
  
ED_Visit_Data %>% 
  ggplot(.,aes(x=week, y=n,  weight= n, color = Period)) +
  geom_point() +
  geom_smooth() +
  ggtitle("ED Visits by Week, All Causes, Pre-/Post-COVID") +
  ylab("Weekly Count") +
  xlab("ED Arrival Date (Week)") +
#  ylim(0,7000) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = c(0.2, 0.2))  +
  scale_x_date(date_breaks = "months")



```


### Plot Inpatient Admission **Counts** by Week, flagged by pre-/post-COVID.

```{r plot-Inpatient-weekly-admissions-counts-with-period-flag}

# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

Admission_Data <- Main_Data %>% 
  dplyr::filter(EdDisposition == "Admit") %>% 
  dplyr::group_by(Period, week = as.Date(cut(EdArrivalDate, "week"))) %>% 
  tally()
  
  
Admission_Data %>%   
  ggplot(.,aes(x=week, y=n, weight= n, color = Period)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Inpatient Admissions by Week, All Causes, Pre-/Post-COVID") +
  ylab("Weekly Count") +
  xlab("ED Arrival Date (Week)") +
#  ylim(0,7000) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = c(0.2, 0.2))  +
  scale_x_date(date_breaks = "months")

```


### Plot Inpatient Admission **Rate** by Week, flagged by pre-/post-COVID.


```{r plot-Inpatient-weekly-admissions-with-period-flag}



# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

ED_Visit_Data <- ED_Visit_Data %>% dplyr::rename(N_Visit = n)
Admission_Data <- Admission_Data %>% dplyr::rename(N_Admit = n)

Rate_Data <- dplyr::left_join(ED_Visit_Data,Admission_Data, by = c("Period","week")) %>% 
  dplyr::mutate(Admission_Rate = round(N_Admit/N_Visit,2)) 
View(Rate_Data)


  
  
Rate_Data %>%   
  ggplot(.,aes(x=week, y=Admission_Rate, weight= N_Visit, color = Period)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Inpatient Admission Rate by Week, All Causes, Pre-/Post-COVID") +
  ylab("Weekly Admission Rate") +
  xlab("ED Arrival Date (Week)") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = c(0.2, 0.2))  +
  scale_x_date(date_breaks = "months") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))




```




## ED Arrivals and Admission **Counts** by Week, flagged by both 
- Alcohol Withdrawal/CHF
- Pre-/post-COVID.

### Table ED Visit Counts by Alcohol Withdrawal and CHF:

```{r}

Main_Data %>% 
  dplyr::group_by(Period,AlcoholWithdrawIndicatedInEncounter,ChfIndicatedInEncounter) %>% 
  tally() %>% 
kable(digits=c(0,4,4,6), align=c("r", 'c','c','r') ,
    caption = "<center><strong>Count of ED Visits by Period (Pre-/Post-COVID), Alcohol Withdrawal and CHF</center></strong>",
    col.names= c("Period", "Alcohol <br/>Withdrawal <br/>Indicated", "CHF <br/>Indicated","Count"),
     escape = FALSE) %>% 
 row_spec(0, bold=T) %>% 
  column_spec(1, width = "3cm", bold = T) %>% 
  column_spec(2:4, width = "1.5cm") %>% 
   kable_styling(position = "center")
# %>% 
#   add_header_above(c("","","","","","", "Hazard Ratio 95% CI" = 2)) %>%
# footnote("") %>%   landscape()



```


### Plot ED Arrivals by Date, flagged by Alcohol Withdrawal/CHF, pre-/post-COVID.

```{r plot-ED-weekly-arrivals-with-period-flag-Alcohol-WD-CHF}

# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

ED_Visit_Data_AlcWD_CHF <- Main_Data %>% 
  dplyr::filter(AlcoholWithdrawIndicatedInEncounter == 1 |
                ChfIndicatedInEncounter == 1 ) %>% 
  dplyr::filter(AlcoholWithdrawIndicatedInEncounter + ChfIndicatedInEncounter < 2) %>% 
  dplyr::mutate(Cause = ifelse(AlcoholWithdrawIndicatedInEncounter == 1, "Alcohol_WD", "CHF")) %>% 
  dplyr::group_by(Period, Cause,week = as.Date(cut(EdArrivalDate, "week"))) %>% 
  tally()

View(ED_Visit_Data_AlcWD_CHF) 
  
ED_Visit_Data_AlcWD_CHF %>% 
  ggplot(.,aes(x=week, y=n,  weight= n, color = Period, linetype = Cause)) +
  geom_point() +
  geom_smooth() +
#  facet_wrap(~Cause, nrow = 1) +
  ggtitle("ED Visits by Week, Alcohol WD/CHF, Pre-/Post-COVID") +
  ylab("Weekly Count") +
  xlab("ED Arrival Date (Week)") +
#  ylim(0,7000) +
  theme(axis.text.x = element_text(angle = 90)) +
#  theme(legend.position = c(0.2, 0.8))  +
  scale_x_date(date_breaks = "months")



```



### Plot Inpatient Admissions **Counts** by Date, flagged by Alcohol Withdrawal/CHF, pre-/post-COVID.

```{r plot-weekly-Inpatient-admissions-with-period-flag-Alcohol-WD-CHF}

# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

Admission_Data_AlcWD_CHF <- Main_Data %>% 
    dplyr::filter(EdDisposition == "Admit") %>% 
  dplyr::filter(AlcoholWithdrawIndicatedInEncounter == 1 |
                ChfIndicatedInEncounter == 1 ) %>% 
  dplyr::filter(AlcoholWithdrawIndicatedInEncounter + ChfIndicatedInEncounter < 2) %>% 
  dplyr::mutate(Cause = ifelse(AlcoholWithdrawIndicatedInEncounter == 1, "Alcohol_WD", "CHF")) %>% 
  dplyr::group_by(Period, Cause,week = as.Date(cut(EdArrivalDate, "week"))) %>% 
  tally()



View(Admission_Data_AlcWD_CHF) 
  
Admission_Data_AlcWD_CHF %>% 
  ggplot(.,aes(x=week, y=n,  weight= n, color = Period, linetype = Cause)) +
  geom_point() +
  geom_smooth() +
#  facet_wrap(~Cause, nrow = 1) +
  ggtitle("Inpatient Admissions by Week, Alcohol WD/CHF, Pre-/Post-COVID") +
  ylab("Weekly Count") +
  xlab("ED Arrival Date (Week)") +
#  ylim(0,7000) +
  theme(axis.text.x = element_text(angle = 90)) +
#  theme(legend.position = c(0.2, 0.8))  +
  scale_x_date(date_breaks = "months")




```





### Plot Inpatient Admission **Rate** by Week, flagged by Alcohol Withdrawal/CHF, pre-/post-COVID.


```{r plot-Inpatient-weekly-admissions-with-period-flag-Alcohol-WD-CHF}



# From: https://stackoverflow.com/questions/40554231/how-to-aggregate-a-dataframe-by-week,
# answer starting with 'Or cut.Date':
# also, https://stackoverflow.com/questions/30018187/changing-tick-intervals-when-x-axis-values-are-dates

ED_Visit_Data_AlcWD_CHF <- ED_Visit_Data_AlcWD_CHF %>% dplyr::rename(N_Visit = n)
Admission_Data_AlcWD_CHF <- Admission_Data_AlcWD_CHF %>% dplyr::rename(N_Admit = n)

Rate_Data_AlcWD_CHF <- dplyr::left_join(ED_Visit_Data_AlcWD_CHF,Admission_Data_AlcWD_CHF, 
by = c("Period","Cause", "week")) %>% 
  dplyr::mutate(Admission_Rate = round(N_Admit/N_Visit,2)) 
View(Rate_Data_AlcWD_CHF)


  
  
Rate_Data_AlcWD_CHF %>%   
    ggplot(.,aes(x=week, y=Admission_Rate,  weight= N_Visit, color = Period)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ Cause, nrow=2) +
  ggtitle("Inpatient Admission Rate by Week, Alcohol WD/CHF, Pre-/Post-COVID") +
  ylab("Weekly Admission Rate") +
  xlab("ED Arrival Date (Week)") +
  theme(axis.text.x = element_text(angle = 90)) +
#   theme(legend.position = c(0.2, 0.2))  +
  scale_x_date(date_breaks = "months") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))



```



```{r add_CY_Quarter-to-Rate_Data_AlcWD_CHF}

Rate_Data_AlcWD_CHF <- Rate_Data_AlcWD_CHF %>% 
  dplyr::mutate(CY_Month = month(week),
                CY_Quarter = case_when(
                  between(CY_Month,1,3) ~ "Q1",
                  between(CY_Month,4,6) ~ "Q2",
                  between(CY_Month,7,9) ~ "Q3",
                  between(CY_Month,10,12) ~ "Q4",
                  TRUE ~ "Problem"
                )
                       )


```



# Run Regression Models

The model will be a Poisson regression, with mean weekly admissions counts dependent on:
The model will be a Poisson regression modeling the counts of weekly admissions
as the dependent variable ('outcome').

The independent variables ('predictors') will be

- Weekly ED visits count.  The more visits, the more admissions would be expected.
- Quarter of the year.  This is to reduce spurious effects due to seasonality.
- Period (pre-/post-COVID)
- Condition:  CHF or Alcohol_WD

There will also be <strong>interactions</strong> added to the model, which will help answer some
key questions.

- Period*Condition:  CHF or Alcohol_WD:  This allows for the change in mean 
weekly admission counts between the pre-COVID and COVID periods to be different 
for the CHF and Alcohol W/D patients.

- Quarter*Condition:  CHF or Alcohol_WD:  This allows for the changes in 
mean weekly admission counts over time periods ('seasonality') to be different 
for the CHF and Alcohol W/D patients.






```{r run-poisson-regression-base-model}

m1 <- glm(Case_Count ~ Patient_Count + 
            Period +  CY_Quarter + Infection_Source + ICU +
            Period*ICU + Period*Infection_Source +  Infection_Source*ICU +
            CY_Quarter*ICU, 
                  family="poisson", data=Matched_Data)





cov.m1 <- vcovHC(m1, type="HC0")
std.err <- sqrt(diag(cov.m1))
r.est <- cbind(Estimate= coef(m1), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(m1)/std.err), lower.tail=FALSE),
LL = coef(m1) - 1.96 * std.err,
UL = coef(m1) + 1.96 * std.err)

r.est


```
