---
title: "How to Make Plots with GGPlot"
author: "Barry DeCicco"
date: '2022-10-15'
output: ioslides_presentation
---


```{r setup, include=FALSE}

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)

# Declare path to this script relative to the project root directory.
here::i_am(
  path = "inst/How to Make Plots with GGPlot.Rmd"
  )

```



```{r load-packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

library(emmeans)    # for emmeans
library(lme4) 
library(flextable)  # for tables with .rtf output
library(psych)      # for ICC
library(magrittr)
library(rmarkdown)  # For pandoc_version()
library(Hmisc)      # for label()
library(here)       # for here()
library(devtools)   # for session_info()
# library(TFCBTLS)    # for git_report()

library(kableExtra) # for pretty tables
library(tidyquant)  # for date conversions - zoo()

library(pastecs)    # for stat.desc
library(tidyverse)

library(readxl)     # For reading in .xlsx and .xsl files, without using Java.
# library(xlsx)       # to import from Excel (cohort dates)


library(janitor)    # for the tabyl command  (nice tables)

library(stringr)    # string work, such as st_detect()

require(gridExtra)  # for printing a grid of plots.

library(broom)      # both of these are for getting nice output
library("tidyr")    # from linear mixed models.

# library("cstatpower")
library("ggplot2")
library("effectsize")
library(hrbrthemes)  # for theme_ipsum()


library(foreign)    # for importing SPSS data sets.
library(robustbase) # for robust MH distances
library(rrcov)

```


# Data Set

## Set up time frame for data:

```{r create-dates-times}


### Create Data for simulated Pre-\Post-COVID study:

#### Create raw vectors:                                     ####
month_sequence_raw <- seq(ymd('2019-03-01'),
                          ymd('2021-02-28'),
                          by='weeks')




Calendar_Date <- rep(month_sequence_raw,100)

Period <- ifelse(Calendar_Date < ymd('2020-03-01'),
                 "Pre-COVID","Post=COVID")

table(Calendar_Date,Period, useNA = 'always')


```



##      Form data set:       

```{r form-data-set}



ER_df <- cbind(as.character(Calendar_Date),Period) %>% 
  as.data.frame() %>% 
  dplyr::mutate(Calendar_Date = as.Date(Calendar_Date)) %>% 
  dplyr::mutate(Quarter_num=quarter(Calendar_Date)) %>% 
  dplyr::mutate(Month_num=as.integer(month(Calendar_Date))) %>% 
  dplyr::select(Calendar_Date, Period, Month_num, Quarter_num) %>% 
  dplyr::mutate(Quarter_effect = case_when(
    Quarter_num == 1 ~ as.integer(2),
    Quarter_num == 2 ~ as.integer(1),
    Quarter_num == 3 ~ as.integer(0),
    Quarter_num == 4 ~ as.integer(0),
    TRUE ~NA_integer_  ),
    Month_effect = case_when(
      Month_num == 1 ~ as.integer(5),
      Month_num == 2 ~ as.integer(5),
      Month_num == 3 ~ as.integer(5),
      Month_num == 4 ~ as.integer(4),
      Month_num == 5 ~ as.integer(2),
      Month_num == 6 ~ as.integer(3),
      Month_num == 7 ~ as.integer(5),
      Month_num == 8 ~ as.integer(5),
      Month_num == 9 ~ as.integer(2),
      Month_num == 10 ~ as.integer(2),
      Month_num == 11 ~ as.integer(4),
      Month_num == 12 ~ as.integer(4),
      TRUE ~NA_integer_  )
  )

```


lapply(ER_df, class)

with(ER_df, table(Month_num,ER_df$Month_effect, 
                  useNA='always'))

hist(ER_df$Month_effect)
#### Set up the COVID and Other Respiratory Rate data:     ####

set.seed(1234567890)

n_rows=nrow(ER_df)

ER_df <- ER_df %>% 
  dplyr::mutate(
    random_other = rpois(n=n_rows, lambda=1),
    random_COVID = rpois(n=n_rows, lambda=2),
    Admissions_Other = Month_effect + Quarter_effect + 
    random_other,
    Admission_COVID = ifelse(Period == "Pre-COVID",0,
      Month_effect + random_COVID)
    )

# View the data set:

View(ER_df)


# Trim the data to needed variables:

ER_df <- ER_df %>% dplyr::select(
  Calendar_Date, Period, Quarter_num, Month_num,
  Admission_COVID,Admissions_Other 
)


View(ER_df)
 
#### Pivot the data                     ####

ER_Long_df <- ER_df %>%  pivot_longer(!c(Calendar_Date, Period, Quarter_num, Month_num),
             names_to = "Cause", values_to = "Count")

View(ER_Long_df)


#### Save the data set.                 ####

save(ER_Long_df, 
     file = "ER_Long_df.Rdata")

# Remove data set; load later:

rm(ER_Long_df)



```


