---
title: "How to Make Plots with GGPlot"
author: "Barry DeCicco"
date: '2022-10-15'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Setting up libraries


```{r setup}

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)

# Declare path to this script relative to the project root directory.
here::i_am(
  path = "inst/How to Make Plots with GGPlot.Rmd"
  )

```


```{r load-packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

library(emmeans)    # for emmeans
library(lme4) 
library(flextable)  # for tables with .rtf output
library(psych)      # for ICC
library(magrittr)
library(rmarkdown)  # For pandoc_version()
library(Hmisc)      # for label()
library(here)       # for here()
library(devtools)   # for session_info()
# library(TFCBTLS)    # for git_report()

library(kableExtra) # for pretty tables
library(tidyquant)  # for date conversions - zoo()

library(pastecs)    # for stat.desc
library(tidyverse)

library(readxl)     # For reading in .xlsx and .xsl files, without using Java.
# library(xlsx)       # to import from Excel (cohort dates)


library(janitor)    # for the tabyl command  (nice tables)

library(stringr)    # string work, such as st_detect()

require(gridExtra)  # for printing a grid of plots.

library(broom)      # both of these are for getting nice output
library("tidyr")    # from linear mixed models.

# library("cstatpower")
library("ggplot2")
library("effectsize")
library(hrbrthemes)  # for theme_ipsum()


library(foreign)    # for importing SPSS data sets.
library(robustbase) # for robust MH distances
library(rrcov)

```


# Data Set

## Set up time frame for data:

```{r create-data-times}


### Create Data for simulated Pre-\Post-COVID study:

#### Create raw vectors:                                     ####
month_sequence_raw <- seq(ymd('2019-03-01'),
                          ymd('2021-02-28'),
                          by='weeks')




Calendar_Date <- rep(month_sequence_raw,100)

Period <- ifelse(Calendar_Date < ymd('2020-03-01'),
                 "Pre-COVID","Post=COVID")

table(Calendar_Date,Period, useNA = 'always')


```

