---
title: "How to Make Plots with GGPlot"
author: "Barry DeCicco"
date: '2022-10-15'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Setting up libraries


```{r setup}

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)

# Declare path to this script relative to the project root directory.
here::i_am(
  path = "inst/How to Make Plots with GGPlot.Rmd"
  )

```


```{r load-packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

library(emmeans)    # for emmeans
library(lme4) 
library(flextable)  # for tables with .rtf output
library(psych)      # for ICC
library(magrittr)
library(rmarkdown)  # For pandoc_version()
library(Hmisc)      # for label()
library(here)       # for here()
library(devtools)   # for session_info()
# library(TFCBTLS)    # for git_report()

library(kableExtra) # for pretty tables
library(tidyquant)  # for date conversions - zoo()

library(pastecs)    # for stat.desc
library(tidyverse)

library(readxl)     # For reading in .xlsx and .xsl files, without using Java.
# library(xlsx)       # to import from Excel (cohort dates)


library(janitor)    # for the tabyl command  (nice tables)

library(stringr)    # string work, such as st_detect()

require(gridExtra)  # for printing a grid of plots.

library(broom)      # both of these are for getting nice output
library("tidyr")    # from linear mixed models.

# library("cstatpower")
library("ggplot2")
library("effectsize")
library(hrbrthemes)  # for theme_ipsum()


library(foreign)    # for importing SPSS data sets.
library(robustbase) # for robust MH distances
library(rrcov)

```


# Data Set

## Load Data from Dropbox

```{r load-date-from-dropbox}

Big_Mart_df <- read.csv("https://www.dropbox.com/s/a7awmqghrb2m145/Big%20Mart%20Dataset%20-%20Sheet1.csv?dl=1")

```



## Examine Data

### Print the first/last rows of the Big Mart data frame?

```{r examine-data-1}

head(Big_Mart_df)
tail(Big_Mart_df)


```

### What are the column names of the Big Mart data frame?

```{r examine-data-2}

names(Big_Mart_df)

```

### What are the classes of the Big Mart data frame?

```{r examine-data-3}
lapply(Big_Mart_df, class)

```

